Lesson 3
========================================================

***

### What to Do First?
Notes:

***

### Pseudo-Facebook User Data
Notes:

```{r Pseudo-Facebook User Data}
pf = read.csv("pseudo_facebook.tsv", sep = "\t")
```

***

### Histogram of Users' Birthdays
Notes:

```{r Histogram of Users\' Birthdays}
library(ggplot2)
qplot(x = dob_day, data = pf, binwidth = 1) + scale_x_continuous(breaks = 1:31)
```

***

#### What are some things that you notice about this histogram?
Response: More people have dob on the 1st day of a month than on other days.
Less people have dob on the 31th day of a month than other days. 

***

### Moira's Investigation
Notes:

***

### Estimating Your Audience Size
Notes:

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response: Conquered the Angels Landing!

#### How many of your friends do you think saw that post?
Response: 50

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response: 40

***

### Perceived Audience Size
Notes:

***
### Faceting
Notes:

```{r Faceting}
qplot(x = dob_day, data = pf, binwidth = 1) +
    scale_x_continuous(breaks = 1:31) +
    facet_wrap(~dob_month)
```

#### Let’s take another look at our plot. What stands out to you here?
Response: The number with dob at Jan 1st is unusually large.

***

### Be Skeptical - Outliers and Anomalies
Notes:

***

### Moira's Outlier
Notes:
#### Which case do you think applies to Moira’s outlier?
Response: bad data about an extreme case

***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
qplot(data = pf, x = friend_count)
```

#### How is this plot similar to Moira's first plot?
Response: There are several users with extremely large number of friends, but most users have smaller number of friends.

***

### Limiting the Axes
Notes:

```{r Limiting the Axes}
qplot(data = pf, x = friend_count, xlim = c(0, 1000))
```

### Exploring with Bin Width
Notes:

***

### Adjusting the Bin Width
Notes:

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
qplot(x = friend_count, data = pf, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50)) +
    facet_wrap(~gender)
```

***

### Omitting NA Values
Notes:

```{r Omitting NA Values}
qplot(x = friend_count, data = subset(pf, !is.na(gender)), binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50)) +
    facet_wrap(~gender)
```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}
by(pf$friend_count, pf$gender, summary)
```

#### Who on average has more friends: men or women?
Response: women

#### What's the difference between the median friend count for women and men?
Response: 22

#### Why would the median be a better measure than the mean?
Response: it's robust to outliers

***

### Tenure
Notes:

```{r Tenure}
qplot(x = tenure, data = pf, color = I("black"), fill = I("#F79420"))
```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}
qplot(x = tenure / 365, data = pf, binwidth = .25, color = I("black"), fill = I("#F79420")) +
    scale_x_continuous(breaks = 0:7, limits = c(0, 7))
```

***

### Labeling Plots
Notes:

```{r Labeling Plots}
qplot(x = tenure / 365, data = pf, binwidth = .25, xlab = "Number of years using Facebook", ylab = "Number of users in sample", color = I("black"), fill = I("#F79420")) +
    scale_x_continuous(breaks = 0:7, limits = c(0, 7))
```

***

### User Ages
Notes:

```{r User Ages}
qplot(x = age, data = pf, binwidth = 1, color = I("black"), fill = I("#5760AB"), xlab = "Age of people using Facebook", ylab = "Number of users in sample") + scale_x_continuous(breaks = seq(0, 113, 5))
```

#### What do you notice?
Response: Most users are around 20. There are a number of users with age around 100.

***

### The Spread of Memes
Notes:

***

### Lada's Money Bag Meme
Notes:

***

### Transforming Data
Notes:

***

### Add a Scaling Layer
Notes:

```{r Add a Scaling Layer}
library(gridExtra)
p1 <- qplot(x = friend_count, data = pf)
p2 <- qplot(x = friend_count, data = pf) + scale_x_log10()
p3 <- qplot(x = friend_count, data = pf) + scale_x_sqrt()
grid.arrange(p1, p2, p3)
```

***


### Frequency Polygons

```{r Frequency Polygons}
qplot(x = www_likes, data = subset(pf, !is.na(gender)), geom = "freqpoly", color = gender) + scale_x_continuous() + scale_x_log10()
```

***

### Likes on the Web
Notes:

```{r Likes on the Web}
by(pf$www_likes, pf$gender, sum)
```


***

### Box Plots
Notes:

```{r Box Plots}
qplot(x = gender, y = friend_count, data = subset(pf, !is.na(gender)), geom = "boxplot")
```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}
qplot(x = gender, y = friend_count, data = subset(pf, !is.na(gender)), geom = "boxplot") + coord_cartesian(ylim = c(0, 1000))
```

***

### Box Plots, Quartiles, and Friendships
Notes:
```{r Box Plots, Quartiles, and Friendships}
qplot(x = gender, y = friend_count, data = subset(pf, !is.na(gender)), geom = "boxplot") + coord_cartesian(ylim = c(0, 300))
```

#### On average, who initiated more friendships in our sample: men or women?
Response: women
#### Write about some ways that you can verify your answer.
Response: The median of friendships_initiated for female is higher than that of male.
```{r Friend Requests by Gender}
qplot(x = gender, y = friendships_initiated, data = subset(pf, !is.na(gender)), geom = "boxplot") + coord_cartesian(ylim = c(0, 150))
by(pf$friendships_initiated, pf$gender, summary)
```

Response:

***

### Getting Logical
Notes:

```{r Getting Logical}
pf$mobile_check_in <- ifelse(pf$mobile_likes > 0, 1, 0)
pf$mobile_check_in <- factor(pf$mobile_check_in)
sum(pf$mobile_check_in == 1) / nrow(pf)
```

Response: 65

***

### Analyzing One Variable
Reflection: I learned the by function to compare between categories.

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!