Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}
library(ggplot2)
pf <- read.csv("../lesson3/pseudo_facebook.tsv", sep = "\t")
qplot(age, friend_count, data = pf)
```

***

#### What are some things that you notice right away?
Response: Most people have small number of friends on Facebook. Some young people have a large number of friends.

***

### ggplot Syntax
Notes:

```{r ggplot Syntax}
ggplot(aes(x = age, y = friend_count), data = pf) +
    geom_point() +
    xlim(13, 90)
```

***

### Overplotting
Notes:

```{r Overplotting}
ggplot(aes(x = age, y = friend_count), data = pf) +
    geom_jitter(alpha = 1 / 20) +
    xlim(13, 90)
```

#### What do you notice in the plot?
Response: Most user have less than 500 friends.

***

### Coord_trans()
Notes:

```{r Coord_trans()}
ggplot(aes(x = age, y = friend_count), data = pf) +
    geom_point(alpha = 1 / 20, position = position_jitter(h = 0)) +
    xlim(13, 90) +
    coord_trans(y = "sqrt")
```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}
ggplot(aes(x = age, y = friend_count), data = pf) +
    geom_point(alpha = 1 / 20) +
    xlim(13, 90) +
    coord_trans(y = "sqrt")
```

#### What do you notice?
The black bars look higher.

***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}
ggplot(aes(x = age, y = friendships_initiated), data = pf) +
    geom_point(alpha = 1 / 10, position = position_jitter(h = 0)) +
    coord_trans(y = "sqrt")
```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}
library(dplyr)
pf.fc_by_age <- pf %>%
    group_by(age) %>%
    summarise(friend_count_mean = mean(friend_count),
              friend_count_median = median(friend_count),
              n = n())
head(pf.fc_by_age)
```

Create your plot!

```{r Conditional Means Plot}
ggplot(aes(x = age, y = friend_count_mean), data = pf.fc_by_age) +
    geom_line()
```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}
ggplot(aes(x = age, y = friend_count), data = pf) +
    geom_point(alpha = 1 / 20, position = position_jitter(h = 0), 
               color = "orange") +
    coord_cartesian(xlim = c(13, 70), ylim = c(0, 1000)) +
    geom_line(stat = "summary", fun.y = mean) +
    geom_line(stat = "summary", fun.y = quantile, fun.args = list(probs = 0.1),
              linetype = 2, color = "blue") +
    geom_line(stat = "summary", fun.y = quantile, fun.args = list(probs = 0.9),
              linetype = 2, color = "blue") +
    geom_line(stat = "summary", fun.y = median, color = "blue")
```

#### What are some of your observations of the plot?
Response: All lines except the 10% quantile have similar trends. The median is smaller than the mean.

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}
cor.test(pf$friend_count, pf$age)
```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(subset(pf, age <= 70), cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}
ggplot(aes(x = www_likes_received, y = likes_received), data = pf) +
    geom_point() +
    coord_cartesian(xlim = c(0, 4e4), ylim = c(0, 1e5))
```

***

### Strong Correlations
Notes:

```{r Strong Correlations}
ggplot(aes(x = www_likes_received, y = likes_received), data = pf) +
    geom_point() +
    xlim(0, quantile(pf$www_likes_received, 0.95)) +
    ylim(0, quantile(pf$likes_received, 0.95)) +
    geom_smooth(method = "lm", color = "red")
```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}
with(pf, cor.test(www_likes_received, likes_received))
```

Response: 0.948

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
library(alr3)
data("Mitchell")
```

Create your plot!

```{r Temp vs Month}
ggplot(aes(x = Month, y = Temp), data = Mitchell) +
    geom_point()
```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot. 0

b. What is the actual correlation of the two variables? 0.057
(Round to the thousandths place)

```{r Noisy Scatterplots}
with(Mitchell, cor.test(Month, Temp))
```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}
ggplot(aes(x = Month, y = Temp), data = Mitchell) +
    geom_point() +
    scale_x_continuous(breaks = seq(0, 203, 12))
```

***

### A New Perspective

What do you notice?
Response: The temperature is periodic every year.

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}
pf$age_with_months <- with(pf, age + 1 - dob_month / 12)
```

***

### Age with Months Means

```{r Age with Months Means}
pf.fc_by_age_months <- pf %>% 
    group_by(age_with_months) %>%
    summarise(friend_count_mean = mean(friend_count),
              friend_count_median = median(friend_count),
              n = n()) %>%
    arrange(age_with_months)
head(pf.fc_by_age_months)
```

Programming Assignment
```{r Programming Assignment}
age_with_months_groups <- group_by(pf, age_with_months)
pf.fc_by_age_months2 <- summarise(age_with_months_groups,
                                  friend_count_mean = mean(friend_count),
                                  friend_count_median = median(friend_count),
                                  n = n())
pf.fc_by_age_months2 <- arrange(pf.fc_by_age_months2, age_with_months)
head(pf.fc_by_age_months2)
```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}
ggplot(aes(x = age_with_months, y = friend_count_mean), 
       data = subset(pf.fc_by_age_months, age_with_months < 71)) +
    geom_line()
```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}
p1 <- ggplot(aes(x = age, y = friend_count_mean), 
       data = subset(pf.fc_by_age, age < 71)) + 
    geom_line() + 
    geom_smooth()
p2 <- ggplot(aes(x = age_with_months, y = friend_count_mean), 
             data = subset(pf.fc_by_age_months, age_with_months < 71)) +
    geom_line() +
    geom_smooth()
p3 <- ggplot(aes(x = round(age / 5) * 5, y = friend_count),
             data = subset(pf, age < 71)) +
    geom_line(stat = "summary", fun.y = mean)
library(gridExtra)
grid.arrange(p1, p2, p3)
```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection: For data with discrete values, it's useful to use jitter and transparency for visualization.

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

